Appendix S1: Supporting Information

### 2021-09-02 ms/SI.Rmd
Fix dendrogram for phylo clusters

# Map taxonomic clusters to grid cells
clusters_tax <-
  biodiv_ferns_spatial %>%
  as_tibble() %>%
  select(grids, cluster = taxonomic_cluster) %>%
  # mutate(cluster = as.character(cluster)) # %>%
  # Convert cluster to numeric to use max() later
  mutate(cluster = levels(cluster)[cluster])

@@

# Map taxonomic clusters to grid cells
clusters_phy <-
  biodiv_ferns_spatial_lumped %>%
  as_tibble() %>%
  select(grids, cluster = phylo_cluster) %>%
  # Convert cluster to numeric to use max() later
  mutate(cluster = levels(cluster)[cluster] %>% as.numeric)

cluster_nodes_phy_tbl <- map_df(1:max(clusters_phy$cluster), ~map_cluster_to_nodes(dendro_phy, clusters_phy, .)) %>%
  mutate(cluster = as.factor(cluster))

# Use the ggtree::`%<+%` operator to map the bootstrap values onto the ggtree object
ggtree(dendro_phy, size = 0.15) %<+% 
  cluster_nodes_phy_tbl +
  aes(color = cluster) +
  scale_color_manual(values = bioregion_cols, na.value = "grey", name = "Cluster") +
  theme(legend.position = "right") +
  labs(subtitle = "**(b)** Phylogenetic") +
  theme(plot.subtitle = element_markdown())
```

>>>>

# Map taxonomic clusters to grid cells
clusters_tax <-
  biodiv_ferns_spatial %>%
  as_tibble() %>%
  select(grids, cluster = taxonomic_cluster) %>%
  # Convert cluster to numeric to use max() later
  mutate(cluster = levels(cluster)[cluster])

@@

# Map phylogenetic clusters to grid cells
clusters_phy <-
  biodiv_ferns_spatial %>%
  as_tibble() %>%
  select(grids, cluster = phylo_cluster) %>%
  # Convert cluster to numeric to use max() later
  mutate(cluster = levels(cluster)[cluster])

cluster_nodes_phy_tbl <- map_df(unique(clusters_phy$cluster), ~map_cluster_to_nodes(dendro_phy, clusters_phy, .)) %>%
  # Lump regions with just a few cells (3 or less)
  mutate(cluster = as.factor(cluster) %>% fct_lump_min(4))

# Use the ggtree::`%<+%` operator to map the bootstrap values onto the ggtree object
ggtree(dendro_phy, size = 0.15) %<+% 
  cluster_nodes_phy_tbl +
  aes(color = cluster) +
  scale_color_manual(
    values = bioregion_cols[c(1,2,3,4,"Other")], breaks = c(1,2,3,4,"Other"), name = "Cluster", na.value = "grey10") +
  theme(legend.position = "right") +
  labs(subtitle = "**(b)** Phylogenetic") +
  theme(plot.subtitle = element_markdown())
```
